Analyses v0.2

### 2020-07-20 R/Plots_manuscript_v0.2.Rmd
Add GDD QTL file to data

for(i in seq_along(subpop_v)){
  snp <- snp_attach(inputfiles$SNPfiles[i])
  phe_df <- read_rds(file.path(inputdir, paste0("G_BLUP_phenotypes_",
                                                "for_gwas_GR_FL_",
                                                names(subpop_v)[i], ".csv")))
  pvdiv_standard_gwas(snp, df = phe_df, type = "linear", outputdir = outputdir,
                      savegwas = TRUE, saveannos = TRUE, txdb = txdb,
                      minphe = 130)
}
```

>>>>

for(i in seq_along(subpop_v)){
  snp <- snp_attach(inputfiles$SNPfiles[i])
  phe_df <- read_csv(file.path(inputdir, paste0("G_BLUP_phenotypes_",
                                                "for_gwas_GR_FL_",
                                                names(subpop_v)[i], ".csv")))
  pvdiv_standard_gwas(snp, df = phe_df, type = "linear", outputdir = outputdir,
                      savegwas = TRUE, saveannos = TRUE, txdb = txdb,
                      minphe = 130)
}
snp_v <- c("12\\.1M", "8\\.8M", "10\\.3M")
# Make output of top 1000 SNPs
for(i in seq_along(subpop_v)){
  snp <- snp_attach(inputfiles$SNPfiles[i])
  gwas_rds <- pvdiv_results_in_folder(path = outputdir, 
                                      pattern = paste0("GWAS_datatable*.*",
                                                       snp_v[i]))
  phenotypes <- str_sub(gwas_rds, start = 16, end = -43)
  out1 <- pvdiv_bigsnp2mashr(path = outputdir, snp = snp, gwas_rds = gwas_rds, 
                             phenotypes = phenotypes, numSNPs = 1000, 
                             clump = FALSE, scaled = FALSE, saveoutput = TRUE,
                             suffix = paste0("GR_FL_", names(subpop_v)[i]))
}

```
# examine top 1000 SNPs
```{r}
gulf_top1000 <- readRDS("~/Github/pvdiv-phenology-gxe/analysis/gwas/G_BLUP/Part-One-Output_Top-Effects-1000-SNPs_GR_FL_Gulf.rds")
gandm_top1000 <- readRDS("~/Github/pvdiv-phenology-gxe/analysis/gwas/G_BLUP/Part-One-Output_Top-Effects-1000-SNPs_GR_FL_Gulf_and_Midwest.rds")
midw_top1000 <- readRDS("~/Github/pvdiv-phenology-gxe/analysis/gwas/G_BLUP/Part-One-Output_Top-Effects-1000-SNPs_GR_FL_Midwest.rds")
```

```{r}
gulf_top1000 %>%
  arrange(desc(max_score_log10p)) %>%
  ungroup() %>%
  #top_n(100, max_score_log10p) %>%
  left_join(log10p_Gulf_top1000) %>%
  #select(-starts_with("GR50"), -starts_with("tmin"), -starts_with("cgdd_12c_10d"), -marker, -CHRN) %>%
  ggplot(aes(x = FL50_G_BLUP_log10p, y = cgdd_12c_10d_G_BLUP_log10p)) +
  geom_point(aes(shape = as_factor(n_cond_in_top_set), color = max_score_log10p),
             size = 2) +
  geom_abline(slope = 1, intercept = 0) +
  scale_color_viridis(end = 0.9, option = "B") +
  scale_shape_manual(values = c(0, 1, 2, 5, 3)) +
  theme(legend.position = "right")
names(log10p_Gulf_top1000)

midw_top1000 %>%
  arrange(desc(max_score_log10p)) %>%
  ungroup() %>%
  #top_n(100, max_score_log10p) %>%
  left_join(log10p_midwest) %>%
  #select(-starts_with("GR50"), -starts_with("tmin"), -starts_with("cgdd_12c_10d"), -marker, -CHRN) %>%
  ggplot(aes(x = FL50_G_BLU_log10p, y = cgdd_12c_gr2fl_G_BLU_log10p)) +
  geom_point(aes(shape = as_factor(n_cond_in_top_set), color = max_score_log10p),
             size = 2) +
  geom_abline(slope = 1, intercept = 0) +
  scale_color_viridis(end = 0.9, option = "B") +
  scale_shape_manual(values = c(0, 1, 2, 5, 3)) +
  theme(legend.position = "right")
names(log10p_midwest)
midw_top1000 %>%
  arrange(desc(max_score_log10p)) %>%
  ungroup() %>%
  top_n(100, max_score_log10p)
```
Midwest has a lot more top hits for these G BLUPs that are at least on the same chromosomes as Li's QTLs. FWIW. GxE may be better, and need to get Li's intervals again and do a formal comparison, but just at first glance. top hits for Midwest are mostly for dyln_fl50...
```{r}
qtl <- read_csv("../data/QTLsWithFlankMarkers_FL50_GDD_7_SITES_Full_model.csv")
qtldf <- qtl %>%
  separate(flank_lo, into = c("CHR", "POS_lo"), sep = "_", convert = TRUE) %>%
  separate(flank_hi, into = c("CHR1", "POS_hi"), sep = "_", convert = TRUE) %>%
  select(-chr, -CHR1, -X1, -lodindex) %>%
  mutate(POS_lo = POS_lo*1000000,
         POS_hi = POS_hi*1000000) %>%
  filter(lodcolumn != "D2F")

i=1
midw_qtl_overlap <- tibble()
gulf_qtl_overlap <- tibble()
gandm_qtl_overlap <- tibble()
for(i in 1:nrow(qtldf)){
  gam_qtl1 <- gandm_top1000 %>%
    filter(CHR == qtldf$CHR[i] & between(POS, qtldf$POS_lo[i], qtldf$POS_hi[i]))
  gulf_qtl1 <- gulf_top1000 %>%
    filter(CHR == qtldf$CHR[i] & between(POS, qtldf$POS_lo[i], qtldf$POS_hi[i]))
  mid_qtl1 <- midw_top1000 %>%
    filter(CHR == qtldf$CHR[i] & between(POS, qtldf$POS_lo[i], qtldf$POS_hi[i]))
  if(i == 1){
    midw_qtl_overlap <- mid_qtl1
    gulf_qtl_overlap <- gulf_qtl1
    gandm_qtl_overlap <- gam_qtl1
  } else {
    midw_qtl_overlap <- midw_qtl_overlap %>%
      full_join(mid_qtl1, by = c("CHR", "POS", "Condition", "max_score_log10p",
                                 "n_cond_in_top_set", "marker", "CHRN"))
    gandm_qtl_overlap <- gandm_qtl_overlap %>%
      full_join(gam_qtl1, by = c("CHR", "POS", "Condition", "max_score_log10p",
                                 "n_cond_in_top_set", "marker", "CHRN"))
    gulf_qtl_overlap <- gulf_qtl_overlap %>%
      full_join(gulf_qtl1, by = c("CHR", "POS", "Condition", "max_score_log10p",
                                 "n_cond_in_top_set", "marker", "CHRN"))

  }
}

nrow(midw_top1000)
midw_qtl_overlap %>%
  arrange(desc(max_score_log10p))
nrow(gandm_top1000)
gandm_qtl_overlap %>%
  arrange(desc(max_score_log10p))
nrow(gulf_top1000)
gulf_qtl_overlap %>%
  arrange(desc(max_score_log10p))
```
How many SNPs are in the QTL regions? And how many SNPs are in the full genome? Therefore how many SNPs would we expect at random?
